---
title: "Question 4"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Jane Doe
Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: null
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
pacman::p_load(huxtable)
pacman::p_load(forcats)
credits = read.csv("D:/User folders/Documents/Practical/21625247/data/netflix/credits.csv")
titles = read.csv("D:/User folders/Documents/Practical/21625247/data/netflix/titles.csv")
merged = full_join(credits, titles, by = "id")
movies = merged %>% filter(type == "MOVIE")
tv = merged %>% filter(type == "SHOW")
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Brief discussion

It is hard to quantify quality and profitability from internet rankings, but it does give us an indication of what is popular. To enter the streaming market, audience scores are extremely important.

# Analytics

```{r}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
good_movie = assess(movies$imdb_score)

popular_movie = assess(movies$imdb_votes)

```

```{r}
#add empty slots for quartiles
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
quarts = empty(movies)
# sort for movie quality
quarts = sorting(quarts,quarts$imdb_score,good_movie,quarts$imdb_votes,popular_movie)
```


```{r}
# Get rid of the fluff
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
tidy_q = tidy_CH(quarts)
illus = table(tidy_q$good_q, tidy_q$pop_q)
illus_df = as.data.frame.matrix(illus)
```

Movies and tv shows can be split into four quartiles along popularity (represented by the amount of IMDB votes) and quality (the IMDB score). Ideally, a streaming service would want films that are at least in the top quartile for one metric and in the top two quartiles for the other.
Older movies and shows are usually cheap to acquire. Combining this with the tier system of the ratings can help management choose films or tv shows that have a higher probability of being successful.
```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
# Only look at the best and most popular older films:
oldies = old_gold(tidy_q,2000)

#Table it
ht =hux(
        Title = oldies$title,
        "Quality Quartile" = oldies$good_q,
        "Popularity Quartile" = oldies$pop_q,
        "Release Year" = oldies$release_year,
        "Genre" = oldies$genres,
        add_colnames = TRUE)
    bold(ht)[1,]           <- TRUE
    bottom_border(ht)[1,]  <- 0.4
    align(ht)[,2]          <- "right"
    right_padding(ht)      <- 10
    left_padding(ht)       <- 10
    width(ht)              <- 0.35
    number_format(ht)      <- 2

    ht
```
Thus a list has been compiled of possible films that can be good contenders to be acquired as a back catalogue for starting up a streaming service.
Obviously newer films and tv shows are also required. To avoid overspending, it is useful to consider what genres are currently popular and would be a good addition to a hypothetical streaming service.
```{r}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
# First we only want newer movies, released after 2017, with a popularity tier of level 4:
newies = new_pop(tidy_q, 2018,4)
genres = newies$genres
action = genre_count(genres, 'action')
romance = genre_count(genres, 'romance')
thriller = genre_count(genres, 'thriller')
comedy = genre_count(genres, 'comedy')
horror = genre_count(genres, 'horror')
drama = genre_count(genres, 'drama')
crime = genre_count(genres, 'crime')
scifi = genre_count(genres, 'scifi')
fantasy = genre_count(genres, 'fantasy')
european = genre_count(genres, 'european')
music = genre_count(genres, 'music')
genre_df = data.frame(genre = c('action','romance','thriller','comedy','horror','drama','crime','scifi','fantasy','european','music'),count = c(action, romance, thriller, comedy,horror,drama,crime,scifi,fantasy,european,music))

```
Based on this graph, drama movies are the most popular and the company should invest in new drama movies for the streaming platform.
```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "\\label{Figure2}", fig.ext = 'png', fig.height = 5, fig.width = 7}
a = barp(genre_df,genre_df$genre,genre_df$count)
print(a)

```

And lastly, it is worth considering the popularity of different age ratings of tv shows over time, as it is important to consider when shows are decided on.
```{r}
    fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
good_show = assess(tv$imdb_score)

popular_show = assess(tv$imdb_votes)
quart_show = empty(tv)
# sort for tv show quality
quart_show = sorting(quart_show,quart_show$imdb_score,good_show,quart_show$imdb_votes,popular_show)
```

```{r}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
tidy_show = tidy_CH(quart_show)
```

```{r}
plot_show = tidy_show %>% arrange(age_certification) %>%group_by(release_year)%>%reframe(avg = mean(imdb_votes, na.rm=T),release_year,age_certification)
```

```{r Figure3,  warning =  FALSE, fig.align = 'center', fig.cap = "\\label{Figure3}", fig.ext = 'png', fig.height = 5, fig.width = 7}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_4/code")
s = plot2(plot_show)
print(s)
```
Based on this figure, there seems to be some nostalgia for shows from 10 years ago, as all of the graphs peak at that point. This is something that can be utilised in a streaming service. There does not, however, seem to be a specific ge category that is vastly more popular.
