---
title: "Question 5"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Jane Doe
Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: null
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
pacman::p_load(huxtable)
#Import data
play_df = read_csv("D:/User folders/Documents/Practical/21625247/data/googleplay/googleplaystore.csv")
reviews_df = read_csv("D:/User folders/Documents/Practical/21625247/data/googleplay/googleplaystore_user_reviews.csv")


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

This report will have two parts:
1. An overview of the success, in terms of downloads, of different app categories over time.
2. An overview of the effect of app size on downloads, and if it could be negative.

# Success of different app categories:
```{r}
# first we have to sort out the download numbers
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_5/code")
play_df = play_df %>% mutate(Installs = gsub('[+]','',Installs)) %>%mutate(Installs = gsub(',','',Installs)) %>%mutate(Installs = strtoi(Installs))
# Solve size as well
play_df = play_df %>% mutate(Size = gsub('[M]','',Size)) %>%mutate(Size = gsub('[Varies with device]','',Size)) %>%mutate(Size = strtoi(Size))
```

```{r}
# Calculate average downloads and reviews for categories
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_5/code")
play_adv = play_df %>% group_by(Genres)%>%reframe(avg_Installs = mean(Installs, na.rm=T),avg_rating = mean(Rating, na.rm=T))
play_adv = unique(play_adv)

```
Here we have a table that illustrates how successful different genre of apps are:
```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_5/code")
ht  =hux(
        Genres = play_adv$Genres,
        "Average amount of Installs" = play_adv$avg_Installs,
        "Average rating" = play_adv$avg_rating,
        add_colnames = TRUE)
    bold(ht)[1,]           <- TRUE
    bottom_border(ht)[1,]  <- 0.4
    align(ht)[,2]          <- "right"
    right_padding(ht)      <- 10
    left_padding(ht)       <- 10
    width(ht)              <- 0.35
    number_format(ht)      <- 2

ht
```
As wel can see from this table, communications are the most successful apps, and the apps with the best reviews are Comic and Board game apps.

# Does app size affect popularity?
```{r}
play_adv = play_df %>% group_by(Genres)%>%reframe(avg_Installs = mean(Installs, na.rm=T),avg_rating = mean(Rating, na.rm=T), Size)
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_5/code")
dl_sizes = assess(play_adv$Size)
print(dl_sizes)
#play_adv = empty(play_adv)
play_adv = sorting(play_adv,play_adv$Size,dl_sizes)
play_2 = play_adv %>% group_by(size_bracket)%>%reframe(avg_Installs=mean(avg_Installs))
```

```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "\\label{Figure2}", fig.ext = 'png', fig.height = 5, fig.width = 7}
barp = barplot(play_2$avg_Installs,
               main = "App ",
               xlab = "Size bracket",
               ylab = "Count",
               names = play_2$size_bracket,
               col = "green")
```
From the figure we can see that the download size of an app does not have a notable effect on its download numbers.