---
title: "Question 2: London"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Jane Doe
Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: null
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
pacman::p_load(huxtable)

london_df = read.csv("D:/User folders/Documents/Practical/21625247/data/London/london_weather.csv")
as_tibble(london_df)
det_df = read.csv("D:/User folders/Documents/Practical/21625247/data/London/UKMonthly_Detailed.csv")

```

<!-- ############################## -->

<!-- # Start Writing here: -->

<!-- ############################## -->

# Introduction \label{Introduction}
Dear friend, I know you want to move to England, but please reconsider. I collected some data and made graphs to convince you, and show you that the weather in England can get quite unpleasant.

# An average day across seasons:
```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_2/code")
london_df = london_df %>% mutate(date = lubridate::ymd(date))
london_df$month<- format(as.Date(london_df$date, format="%Y-%m-%d"),"%B")
#london_sea = london_df %>% mutate(month =format(months.Date(date)))
london_sea = season(london_df)
print(london_sea)

ht =hux(
        Season = london_sea$season,
        Sunshine = london_sea$sunshine,
        "Average Maximum Temperature" = london_sea$max_temp,
        "Average Mean Temperature" = london_sea$mean_temp,
        "Average Minimum Temperature" = london_sea$min_temp,
        "Average Daily Precipitation" = london_sea$precipitation,
        add_colnames = TRUE)
    bold(ht)[1,]           <- TRUE
    bottom_border(ht)[1,]  <- 0.4
    align(ht)[,2]          <- "right"
    right_padding(ht)      <- 10
    left_padding(ht)       <- 10
    width(ht)              <- 0.35
   number_format(ht)      <- 2

      ht
```
Compared to South Africa, average temperatures remain fairly cool. Even in summer, the average maximum temperature is just 22 degrees, and winters are almost always very cold with very little sunlight.

# The chances of rain across the year:
```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "\\label{Figure2}", fig.ext = 'png', fig.height = 5, fig.width = 7}
fmxdat::source_all("D:/User folders/Documents/Practical/21625247/Question_2/code")
london_rain = rain(london_df)
avg_rain = mean(london_rain$rain,na.rm=T)
w =london_plot(london_rain,london_rain$rain,"","Probability of Rain", "Probability of at least 1 mm of rain falling")
print(w)
```
As you can see, most days of the year there is a fair chance of having at least 1 mm of rain, so you are likely to encounter a lot of rain in England.




